Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-10-20 paper/main.tex
formatting of comments and cleanup

\textbf{[Was mir hier nicht gefällt, ist, dass du von Parameter schätzen bei ABMs kommend ziemlich detailliert über Mechanik redest. Das passt nicht. Man erwartet mehr Infos über den Blueprint und ist verwirrt. Worum geht es hier?]}

@@

% \input{introduction_old}

@@

\textbf{[Ich denke nicht, dass $\vec{x}_i$ hier nötig ist. Es bietet keinerlei Information. Du kannst alles so schreiben ohne das mathematische Symbol. Du musst den Bogen hinbekommen von dem allgemeinen Problem des Parameterschätzen bei ABMs zu dem spezifischen Problem, welches du hier verhandelst.]}

% \begin{itemize}
%     \item This publication contains 5 things:
%     \begin{enumerate}
%         \item Methods of how to obtain data from microscopic images and perform parameter
%             estimations; $\rightarrow$ also possibly across multiple generations
%         \item Showcase the usefulness of the methods and the model by applying it to parameter
%             estimation via microscopic images and multilayer formation
%         \item Initial (incomplete) model of rod-shaped bacteria
%         \item Generate 3D Images (masks)
%         \item A python package which can do all of that and can be reused and extended
%     \end{enumerate}
%     \item Overall structure
%     \begin{enumerate}
%         \item users bring model + data
%         \item this paper provides methods to do the parameter estimation + visualization
%     \end{enumerate}
%     \item For complete model, more work has to be done
%     \begin{itemize}
%         \item More aspects (see Review; put in discussion)
%         \item Note that we only care about \textit{E.Coli} and \textit{B.Subtilits}! This is
%             important.
%     \end{itemize}
%     \begin{itemize}
%         \item State of the Art
%     \end{itemize}
% \end{itemize}

@@

While some rod-shaped bacteria grow by inserting new material at the ends, \textit{E.Coli} and
\textit{B.Subtilis} utilize a method where new material is inserted along the cylindrical part of
the rod. The details of the division event (i.e. Z-Ring formation) are very intricate and are heavily
studied as a subject on their own~\cite{Harry2001}.
On a higher level view, the rod is split apart at a point close to the center of the cell, thus
creating two new daughter cells.
We know that the best predictor for when the division event occurs, is the length of the rod as
opposed to the age of bacterium~\cite{Robert2014}.
Furthermore, not only the growth of the whole colony but also the growth of individual bacteria is
exponential~\cite{Amir2014,Takeuchi2005}.
\textbf{[Bitte etwas kürzen, da du hier keinen Review schreibst und dich deswegen um Prägnanz bemühen musst.]}

>>>>

\textbf{
    Was mir hier nicht gefällt, ist, dass du von Parameter schätzen bei ABMs kommend ziemlich
    detailliert über Mechanik redest.
    Das passt nicht.
    Man erwartet mehr Infos über den Blueprint und ist verwirrt.
    Worum geht es hier?
}

@@

@@

\textbf{
    Du musst den Bogen hinbekommen von dem allgemeinen Problem des Parameterschätzen bei ABMs zu dem
    spezifischen Problem, welches du hier verhandelst.
}

@@

While some rod-shaped bacteria grow by inserting new material at the ends, \textit{E.Coli} and
\textit{B.Subtilis} utilize a method where new material is inserted along the cylindrical part of
the rod. The details of the division event (i.e. Z-Ring formation) are very intricate and are heavily
studied as a subject on their own~\cite{Harry2001}.
On a higher level view, the rod is split apart at a point close to the center of the cell, thus
creating two new daughter cells.
We know that the best predictor for when the division event occurs, is the length of the rod as
opposed to the age of bacterium~\cite{Robert2014}.
Furthermore, not only the growth of the whole colony but also the growth of individual bacteria is
exponential~\cite{Amir2014,Takeuchi2005}.
\textbf{
    Bitte etwas kürzen, da du hier keinen Review schreibst und dich deswegen um Prägnanz bemühen
    musst.
}
